### 2019-05-10 paper/paper.tex
WIP

Software engineering has for two decades, experimented with the concept of distributing software in faster release cycles; endeavoring to do so without sacrificing reliability and security. To achieve such a goal, there has been a widespread movement in the technical community to advocate for using Agile practices, and in particular: continuous integration, delivery, and deployment. The traditional methods of software development no longer meet the need of businesses that -- now more than ever -- want to proactively engage and retain their customers. The organizational transition to Agile practices demands a large mentality change and require individuals to recognize software as incremental features developed with cross-collaboration of small comprehensive team units, as opposed to large modules developed by siloed units.

\section{Constitution of Continuous Software Engineering Practices}
The word 'Agile' can be quite a jumbled terminology depending who a person talks to. Software professionals have their own experiences and stories of using it in their day-to-day work with varying degrees of opinions and outcomes. The Agile Manifesto is a declaration of the principles of Agile, which attempts to alleviate any misunderstanding of what it means to be Agile in a software context. One principle of the Agile Manifesto states that the highest priority is satisfying customers with early and often continuous delivery \cite[p. ~50]{meyer_2014}. It is apparent that at the heart of Agile is the value of producing software quickly and efficiently, without sacrificing a team's sustainability. One such software development method that has been in existence for over two decades, and fundamentally a practical expression of the principles of the Agile Manifesto, is Extreme Programming (XP).

@@

Of the ideal software practices come commonly known and used vocabulary: continuous integration, delivery, and deployment. Many software professionals however, have misunderstood the these development practices and at times, infuse them as one concept without careful and thoughtful distinction. It would therefore, be wise to define each component for what they represent and why it matters.

@@

It is absolutely crucial to note that using continuous delivery is state-dependent practice on continuous integration. The purpose of continuous delivery is to provision the software product to an production-like environment meant for acceptance testing by stakeholders such as the customers. The stakeholders are the main drivers for the decision of whether the software product can go into a real production environment. In the case that it is accepted, a manual process will be used to deploy it to production. The benefits of continuous delivery include reduced deployment risks, faster user feedback, and overall lower project costs \cite[p. ~3910-3911]{shahin_babar_zhu_2017}.

@@

Software professionals however, often get these three continuous software engineering practices confused or often times do not understand the deeper details that differentiate one from another. For example, Kofi Senaya, Director of Product from Clearbridge Mobile says "continuous Integration means that when [developers] are working on the same code, they are building and unit-testing it to prevent any integration problems" \cite{stackify_2018}. The first misunderstanding from Kofi is that he implies continuous integration only runs unit tests against the source code. Other levels of testing such as integration and system testing can also be implemented for continuous integration. The second misunderstanding is the implication that unit tests will cover all cases of integration functionality. There is a reason that integration tests exist, and that is for testing that module-to-module interaction works as intended.

>>>>

The software engineering community has for a few decades experimented with the concept of distributing software in faster release cycles; endeavoring to do so without sacrificing reliability and security. To achieve such a goal, there has been a widespread movement in the technical community to advocate for using Agile practices, and in particular: continuous integration, delivery, and deployment. The traditional methods of software development no longer meet the need of businesses that -- now more than ever -- want to proactively engage and retain their customers. The organizational transition to Agile practices demands a large mentality change and require individuals to recognize software as incremental features developed with cross-collaboration of small comprehensive team units, as opposed to large modules developed by siloed units.

\section{Constitution of Continuous Software Engineering Practices}
The word 'Agile' can be quite a jumbled terminology depending whom a person talks to. Software professionals have their own experiences and stories of using it in their day-to-day work with varying degrees of opinions and outcomes. The Agile Manifesto is a declaration of the principles of Agile, which attempts to alleviate any misunderstanding of what it means to be Agile in a software context. One principle of the Agile Manifesto states that the highest priority is satisfying customers with early and often continuous delivery \cite[p. ~50]{meyer_2014}. It is apparent that at the heart of Agile is the value of producing software quickly and efficiently, without sacrificing a team's sustainability. One such software development method that has been in existence for over two decades, and fundamentally a practical expression of the principles of the Agile Manifesto, is Extreme Programming (XP).

@@

Of the ideal software practices that are commonly known and trending vocabulary -- continuous integration, delivery, and deployment -- come with the responsibility of defining them. Many software professionals, however, have misunderstood these development practices and at times, infuse them as one concept without careful and thoughtful distinction. It would, therefore, be wise to define each component for what they represent and why it matters.

@@

It is absolutely crucial to note that using continuous delivery is state-dependent practice on continuous integration. The purpose of continuous delivery is to deploy a software product to a production-like environment meant for acceptance testing by stakeholders such as the customers. The stakeholders are the main drivers for the decision of whether the software product can go into a real production environment. In the case that it is accepted, a manual process will be used to deploy it to production. The benefits of continuous delivery include reduced deployment risks, faster user feedback, and overall lower project costs \cite[p. ~3910-3911]{shahin_babar_zhu_2017}.

@@

Software professionals, however, often get these three continuous software engineering practices confused or often times do not understand the deeper details that differentiate one from another. For example, Kofi Senaya, Director of Product from Clearbridge Mobile says "continuous Integration means that when [developers] are working on the same code, they are building and unit-testing it to prevent any integration problems" \cite{stackify_2018}. The first misunderstanding from Kofi is that he implies continuous integration only runs unit tests against the source code. Other levels of testing such as integration and system testing can also be implemented for continuous integration. The second misunderstanding is the implication that unit tests will cover all cases of integration functionality. There is a reason that integration tests exist, and that is for testing that module-to-module interaction works as intended. The third misunderstanding is stating that the developers are building and unit testing the software. The statement assumes that continuous integration is a manual process by which the developers partake in compiling and then running tests against the software. Kofi then goes on to say that "the code is verified by the automated build which allows teams to identify problems" \cite{stackify_2018}, which conflicts with the previous statement. It is clear that explaining the uniquity of these continuous software engineering practices is a challenge for software professionals.

An added layer of complexity that makes defining what it means to do continuous software engineering more difficult is the well-documented phenomena of software developers and software researchers non-collaboration.
